Direct Spectroscopic Detection: A Cheap Method to Detect and Characterize Binary Systems

### 2015-10-09 paper/ms.tex
Updated Acknowledgments and accented stuff.

\begin{abstract}
Young, intermediate-mass stars are experiencing renewed interest as targets for direct-imaging planet searches. However, these types of stars are part of multiple systems more often than not. Close stellar companions affect the formation and orbital evolution of any planets, and the properties of the companions can help constrain the binary formation mechanism. Unfortunately, close companions are difficult and expensive to detect with imaging techniques. In this paper, we describe the direct spectroscopic detection method wherein a high resolution spectrum of the primary is cross-correlated against a template for a companion star. Variants of this method have previously been used to search for stellar, brown dwarf, and even planetary companions. We show that the direct spectral detection method can detect companions as late as M-type orbiting A0 or earlier primary stars in a single epoch on small aperture telescopes. In addition to estimating the detection limits, we determine the sources of uncertainty in characterizing the companion temperature, and find that large systematic biases can exist. After calibrating the systematic biases with synthetic binary star observations, we apply the method to a sample of 34 known binary systems with an A- or B-type primary star. We detect nine total companions, including four of the five known companions with literature temperatures between $4000$ K $ < T < 6000$ K, the temperature range for which our method is optimized. We additionally characterize the companion for the first time in two previously single-lined binary systems and one binary identified with speckle interferometry. This method provides an inexpensive way to use small aperture telescopes to detect binary companions with moderate mass-ratios, and is competitive with imaging techniques inside $\sim 100-200$ mas.
\end{abstract}

@@

\label{sec:intro}
There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby $\sim 2 M_{\odot}$ stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits. In this context, binary companions are contaminants; companions complicate radial velocity planet searches because they necessitate simultaneous modeling of both stellar motions \citep[e.g.][]{Bergmann2015}. Likewise, companions complicate direct imaging planet searches by requiring either extremely high contrast instrumentation \citep{Thalmann2014} or specialized coronagraphs \citep{Crepp2010}.

@@

 One technique that is separation independent is to search directly for the composite spectrum of two stars. \citet{Burgasser2007} used single-epoch low resolution spectroscopy to identify and characterize a brown dwarf binary system by fitting both spectra simultaneously. This method only works if the stars have a similar brightness but very different spectra, such that the spectral features from both components are visible and distinguishable. If, as in the case of binary systems with very large flux ratios, the companion spectrum is buried within the noise of the primary star then a different method is needed.

The direct spectroscopic detection method, and variations thereof, has been used to search for binary companions to early B-stars \citep{Gullikson2013}, main sequence FGK-stars \citep{Kolbl2015}, young K-M stars \citep{Prato2002}, and even `Hot Jupiter' type planets \citep{Snellen2010, Brogi2012, deKok2013} orbiting FGK-stars. The method relies on the cross-correlation function (CCF) of a high spectral resolution spectrum of the primary star with a model spectrum for the expected companion. Since the CCF uses every pixel in the spectrum, and more importantly every spectral line in the secondary spectrum, the detection significance increases approximately as $\sqrt{N}$, where N is the number of spectral lines. For high resolution cross-dispersed echelle spectra, this amplification can reach factors of 10, allowing the detection \emph{and characterization} of a secondary spectrum where the individual lines are completely buried in noise. Since the direct spectroscopic detection method uses a seeing-limited spectrum of the primary star, its sensitivity is independent of separation inside $\sim 1 ''$ and can make use of small telescopes to detect high contrast companions.

In this paper, we describe the direct spectroscopic detection method in detail, and use it to detect the secondary star in nine known binary systems. We describe the method in Section \ref{sec:method}. We describe the observations and data reduction in Section \ref{sec:obs}, then use the observations to estimate the accuracy with which we can measure the companion temperature in Section \ref{subsec:systematics} and the sensitivity of the method in Section \ref{subsec:sensitivity}. In Section \ref{sec:results} we use the direct spectroscopic method to search for known companions, and discuss the results in Section \ref{sec:conclusions}.

@@

All implementations of the direct spectroscopic method use high spectral resolution and high signal-to-noise spectra, and search for companions with extreme flux ratios by cross-correlating the observed spectra with models for the expected companion. The main differences between the various implementations are the primary star and telluric line removal processes. The `Hot Jupiter' searches \citep[e.g.][]{Snellen2010} use known orbital phase information and a high degree of phase coverage to simultaneously estimate an empirical stellar and telluric spectrum with minimal contamination from the planet, while \cite{Kolbl2015} subtract a best-fit model spectrum for the primary star. Since \cite{Kolbl2015} use optical data, they do not attempt any telluric correction. Note that the approach of \cite{Kolbl2015} is conceptually similar to the todcor code \citep{Mazeh1994}, which is widely used to search for double-lined spectroscopic binary systems.

@@

\begin{equation}
w = \frac{v\sin{i} \cdot f}{c} \cdot \frac{\lambda_0}{\Delta \lambda}
\label{eqn:smoothing}
\end{equation}
where $v\sin{i}$ is the literature rotational velocity of the star, $\lambda_0$ is the central wavelength of the echelle order, $\Delta \lambda$ is the wavelength spacing per pixel of the order, $c$ is the speed of light, and $f = 0.25$ is an empirically determined parameter to give a visually adequate fit. Typical window sizes ranged from 50 - 100 pixels.

@@

\begin{itemize}
\item $\rm T_{eff} = 3000-7000$ K\footnote{We extend the grid to higher temperatures if the measured temperature (see Section \ref{subsec:systematics}) is near 7000 K}, in steps of 100 K
\item {[}Fe/H{]} = -0.5, 0.0, +0.5
\item $v\sin{i} = 1, 5, 10, 20, 30 \ \rm km \ s^{-1}$
\end{itemize}
Here, the $v\sin{i}$ is the rotational velocity of the secondary star. We account for the small influence that the smoothing kernel has on the companion spectrum by convolving the model with the same smoothing kernel used for the data, and subtracting the convolved model from the original. Treating the model spectrum in this way is more commonly known as unsharp masking. Finally, we cross-correlate every echelle order that does not have strong telluric residuals against the corresponding model spectrum, and combine the CCFs for each order using a simple average. The method is summarized below:

\begin{enumerate}
 \item Smooth the observed spectrum with a Gaussian smoothing kernel with width given by Equation \ref{eqn:smoothing}, and subtract the smoothed spectrum from the original
 \item Rotationally broaden the Phoenix model spectrum to the requested companion $v\sin{i}$
 \item Smooth the broadened spectrum to the instrumental resolution by convolving it with a gaussian kernel of appropriate width.
 \item Unsharp mask the broadened model spectrum
 \item Resample the processed model spectrum to the same wavelength spacing per pixel as the observed spectrum.
 \item Cross-correlate each echelle order against the corresponding processed model spectrum, and combine using a simple average.
\end{enumerate}

@@

The second dataset (Table \ref{tab:latecal}) contains F-M type stars which have a high-quality temperature estimate in the literature. We use the first two samples in Sections \ref{subsec:systematics} and \ref{subsec:sensitivity} to assess the accuracy of the temperature estimation using the direct spectral detection method and the sensitivity to companions of various temperatures.

@@

We estimate the expected companion temperature depending on whether it is part of a spectroscopic (Table \ref{tab:specdata}) or visual (Table \ref{tab:imagedata}) binary system. In the case of double-lined spectroscopic binaries, we use the ratio of the semi-amplitudes given in the 9th catalog of spectroscopic binary orbits \citep[SB9,][]{SB9} to estimate the mass-ratio of the system. We convert the primary star spectral type from the Simbad database \citep{Simbad} to mass by interpolating Table 5 of \citet{Pecaut2013}. The mass-ratio and primary mass gives an estimate of the companion mass, which we convert to temperature by interpolating the same table. Most of the directly-imaged binary systems do not have orbital information, so we use the magnitude difference published in the Washington Double Star catalog \citep[WDS, ][]{WDS}. We use the Simbad spectral type of the primary star and Table 5 of \citet{Pecaut2013} to estimate the primary star temperature ($T_1$) and radius ($R_1$). We then find the companion temperature that minimizes the following function for the companion temperature ($T_2$), given the observed magnitude difference ($\Delta m_{obs}$)
\begin{equation}
Q = (m(T_2, R_2) - m(T_1, R_1) - \Delta m_{obs})^2
\label{eqn:secteff}
\end{equation}
where $m(T, R)$ is the Vega magnitude of a star with temperature T and radius R. We use the pysynphot package\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} and a Kurucz model grid \citep{Castelli2003} to calculate $m(T, R)$, and assume the companion is on the main sequence to estimate its radius ($R_2$). For both spectroscopic and visual binary systems, we assume spectral type uncertainties of $\pm 1$ subtype on the primary stars, and propagate the uncertainties into uncertainty in the companion temperature. We include the binary system in the sample if the median companion temperature is $< 7500$ K.

We use the same set of instruments and settings for all observations throughout the three datasets. We use the CHIRON spectrograph \citep{CHIRON} on the 1.5m telescope at Cerro Tololo Inter-American Observatory for all southern targets. This spectrograph is an $R\equiv \lambda / \Delta \lambda = 80000$ cross-dispersed echelle spectrograph with wavelength coverage from 450 - 850 nm, and is fed by a $2.7''$ optical fiber. The data are automatically reduced with a standard CHIRON data reduction pipeline, but the pipeline leaves residuals of strong lines in adjacent orders. We bias-correct, flat-field and extract the spectra with the optimum extraction technique \citep{Horne1986} using standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and use the wavelength calibration from the pipeline reduced spectra.

For the northern targets, we use a combination of the High Resolution Spectrograph \citep[HRS,][]{HRS} on the Hobby Eberly Telescope, and the Tull coude \citep[TS23,][]{TS23} and IGRINS \citep{IGRINS} spectrographs, both on the 2.7m Harlan J. Smith Telescope. All three northern instruments are at McDonald Observatory. For the HRS, we use the $R = 60000$ setting with a $2''$ fiber, and with wavelength coverage from 410-780 nm. We bias-correct, flat-field, and extract the spectra using an IRAF pipeline. The HRS spectra are wavelength-calibrated using a Th-Ar lamp observed immediately before or after the science observations.

For the TS23, we use a $1.2''$ slit in combination with the E2 echelle grating (53 grooves/mm, blaze angle $65^{\circ}$), yielding a resolving power of $R=60000$ and a wavelength coverage from 375-1020 nm. We reduce the data using an IRAF pipeline very similar to the one we use for the HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.

@@

\begin{figure}
        \centering
        \subfigure[TS23]{
            \label{fig:error:a}
            \includegraphics[scale=0.45]{TS23_simple_Tact2Tmeas.pdf}
         }
         \subfigure[HRS]{
             \label{fig:error:b}
             \includegraphics[scale=0.45]{HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{fig:error:c}
             \includegraphics[scale=0.45]{IGRINS_simple_Tact2Tmeas.pdf}
         }
         \subfigure[CHIRON]{
             \label{fig:error:d}
             \includegraphics[scale=0.45]{CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectroscopic detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subsec:systematics}), and the blue lines are the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{fig:error}
\end{figure}

@@

Each synthetic binary observation contributes a pair of measured and actual (literature) companion temperatures, and so each late-type star in Table \ref{tab:latecal} has many independent temperature measurements made with the direct spectral detection method. To determine the correspondence between measured and actual temperature, we perform a Markov Chain Monte Carlo (MCMC) fit to a straight line using the emcee code \citep{emcee}. We plot the mean and standard deviation of the measured temperatures in Figure \ref{fig:error}, along with 300 MCMC samples for the linear fit and the line of unity slope. The MCMC samples give posterior probability distributions for the parameters $a$ and $b$ relating the actual temperature ($T_a$) to the measured temperature ($T_m$) through

@@

The typical temperature uncertainty with the direct spectroscopic method is $\sim 150 - 200$ K, but the optical instruments systematically overestimate the companion temperature. \emph{The error analysis is therefore not just important to measure the parameter uncertainties, but also to get the correct answer.} We suspect the systematic biases come from a mismatch between the Phoenix model spectrum template and the real spectrum of a late-type star. The biases are different for each instrument because the instruments have different wavelength ranges, and so the spectral lines that contribute most to the cross-correlation function are different.

@@

By combining the sensitivity calculations described above with the $v\sin{i}$ samples, we marginalize over the expected rotation periods of the secondary stars to get simpler curves of detection rate as a function of companion star temperature. We show the median and approximate range of the marginalized detection rate in Figure \ref{fig:sensitivity}. The direct spectral detection method can reliably detect companions as cool as 3700 K in most cases, although the primary star spectral type plays a dominant role in setting the coolest detectable companion.

@@

We now use the direct spectroscopic detection method to measure the temperatures of several known binary systems (Table \ref{tab:known}). We cross-correlate the spectra against the full grid of model spectra enumerated in Section \ref{sec:method}, and find the temperature using Equation \ref{eqn:tmeas}. We then convert the measured temperature to PDFs of the true companion temperature using the MCMC chains developed in Section \ref{subsec:systematics} (see also Figure \ref{fig:error}). For stars with multiple observations, we multiply the PDFs from each detection. Finally, we calculate the companion temperature and confidence interval from the integral of the PDF:

@@

We compare our companion temperature measurements from the direct spectral detection method to the estimates described above in Figure \ref{fig:known}. There is overall excellent agreement between the temperatures, with most points falling within $1 \sigma$ of equality. We test for a bias ($\Delta$) between the measured temperatures ($T_m$) and expected temperatures ($T_a$) with the equations

@@

\section{Discussion and Conclusions}
\label{sec:conclusions}
We have presented and extensively characterized the direct spectral detection method for finding companions to intermediate-mass stars using high resolution cross-dispersed echelle spectroscopy. Using a very large number of synthetic but realistic binary star observations, we have constrained the uncertainty and systematic errors present in determining the companion temperature with the direct spectral detection method. The typical uncertainties are on the order of 200 K across all instruments used in this study, with a systematic offset of similar magnitude (for the optical instruments). We use the synthetic binary star analysis to calibrate the direct spectral detection method for the four instruments used in this study between the temperatures $ 3500 K < T < 6500 K$.

We also estimate the sensitivity to detection of companions with a range of temperature and $v\sin{i}$ by creating a second set of synthetic companions. The method can detect companions as late as M0 in most cases, although the lower limit depends on the primary star spectral type, the signal-to-noise ratio achieved, and the instrument used. The median detection limit corresponds to flux ratios as small as $F_{\rm  sec}/F_{\rm prim} \sim 10^{-3}$ and binary mass-ratios $M_{\rm  sec}/M_{\rm prim} \sim 0.2$, or a main-sequence M0 star orbiting an A0V primary.

The lowest detectable mass-ratio is even more striking for young stars. At 1 Myr, both the A0 star and its companion are still contracting onto the main sequence \citep{Bressan2012}. The flux ratio limit corresponds to a $\sim$ M1 companion, similar to the main sequence case. However the mass-ratio in this young system is $M_{\rm  sec}/M_{\rm prim} \sim 0.1$, half that of main-sequence components with similar spectral types. The direct spectral detection method is therefore well suited for finding close, low-mass companions to massive young stars.

There is also an upper limit on the detectable companions set by rotation. Our method of removing the primary star spectrum can also remove the companion spectrum if it has a similar rotational velocity. Subtracting a model atmosphere for the primary star would remove the upper limit, but would reduce the detection rate for cool companions that are most difficult to detect with any other means.

Finally, we applied the direct spectral detection method to a set of known binary systems with close, late-type companions. We detect the companion spectrum in 9 of the binary systems, 3 of which are new detections. Most of the companions we fail to detect are likely very cool, falling below the sensitivity limit of our data.

@@

The Hobby-Eberly Telescope (HET) is a joint project of the University of Texas at Austin, the Pennsylvania State University, Stanford University, Ludwig-Maximilians-Universitat Munchen, and Georg-August-Universitat Gottingen. The HET is named in honor of its principal benefactors, William P. Hobby and Robert E. Eberly.

@@

\bibliography{references}

@@

\enddata
%\vspace{-0.8cm}
\tablecomments{Known binary stars detected through either high contrast imaging or interferometry. The imaging data comes from the Washington Double Star Catalog \citep{WDS}, and the most recent measurements are given as superscripts to the star name: [1]: \cite{McAlister1989}; [2]: \cite{Roberts2007}; [3]: \cite{Hipparchos}; [4]: \cite{Mamajek2010}; [5]: \cite{Drummond2014}; [6]: \cite{Shatsky2002}; [7]: \cite{Tokovinin2010}; [8]: \cite{McAlister1987}; [9]: \cite{Horch2010}; [10]: \cite{Horch2008}; [11]: \cite{Horch2001}; [12]: \cite{DeRosa2012}
}
\end{deluxetable}

@@

>>>>

\begin{abstract}
Young, intermediate-mass stars are experiencing renewed interest as targets for direct-imaging planet searches. However, these types of stars are part of multiple systems more often than not. Close stellar companions affect the formation and orbital evolution of any planets, and the properties of the companions can help constrain the binary formation mechanism. Unfortunately, close companions are difficult and expensive to detect with imaging techniques. In this paper, we describe the direct spectral detection method wherein a high-resolution spectrum of the primary is cross-correlated against a template for a companion star. Variants of this method have previously been used to search for stellar, brown dwarf, and even planetary companions. We show that the direct spectral detection method can detect companions as late as M-type orbiting A0 or earlier primary stars in a single epoch on small-aperture telescopes. In addition to estimating the detection limits, we determine the sources of uncertainty in characterizing the companion temperature, and find that large systematic biases can exist. After calibrating the systematic biases with synthetic binary star observations, we apply the method to a sample of 34 known binary systems with an A- or B-type primary star. We detect nine total companions, including four of the five known companions with literature temperatures between $4000$ K $ < T < 6000$ K, the temperature range for which our method is optimized. We additionally characterize the companion for the first time in two previously single-lined binary systems and one binary identified with speckle interferometry. This method provides an inexpensive way to use small-aperture telescopes to detect binary companions with moderate mass-ratios, and is competitive with imaging techniques inside $\sim 100-200$ mas.
\end{abstract}

@@

\label{sec:intro}
There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby $\sim 2 M_{\odot}$ stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits. In this context, binary companions are contaminants; companions complicate radial velocity planet searches because they necessitate simultaneous modeling of both stellar motions \citep[e.g.][]{Bergmann2015}. Likewise, companions complicate direct imaging planet searches by requiring either extremely high-contrast instrumentation \citep{Thalmann2014} or specialized coronagraphs \citep{Crepp2010}.

@@

 One technique that is separation independent is to search directly for the composite spectrum of two stars. \citet{Burgasser2007} used single-epoch low-resolution spectroscopy to identify and characterize a brown dwarf binary system by fitting both spectra simultaneously. This method only works if the stars have a similar brightness but very different spectra, such that the spectral features from both components are visible and distinguishable. If, as in the case of binary systems with very large flux ratios, the companion spectrum is buried within the noise of the primary star then a different method is needed.

The direct spectral detection method (hereafter referred to as the DSD method), and variations thereof, has been used to search for binary companions to early B-stars \citep{Gullikson2013}, main sequence FGK-stars \citep{Kolbl2015}, young K-M stars \citep{Prato2002}, and even `Hot Jupiter' type planets \citep{Snellen2010, Brogi2012, deKok2013} orbiting FGK-stars. The method relies on the cross-correlation function (CCF) of a high-spectral-resolution spectrum of the primary star with a model spectrum for the expected companion. Since the CCF uses every pixel in the spectrum, and more importantly every spectral line in the secondary spectrum, the detection significance increases approximately as $\sqrt{N}$, where N is the number of spectral lines. For high-resolution cross-dispersed \'echelle spectra, this amplification can reach factors of 10, allowing the detection \emph{and characterization} of a secondary spectrum where the individual lines are completely buried in noise. Since the DSD method uses a seeing-limited spectrum of the primary star, its sensitivity is independent of separation inside $\sim 1 ''$ and can make use of small telescopes to detect high-contrast companions.

In this paper, we describe the DSD method in detail, and use it to detect the secondary star in nine known binary systems. We describe the method in Section \ref{sec:method}. We describe the observations and data reduction in Section \ref{sec:obs}, then use the observations to estimate the accuracy with which we can measure the companion temperature in Section \ref{subsec:systematics} and the sensitivity of the method in Section \ref{subsec:sensitivity}. In Section \ref{sec:results} we use the DSD method to search for known companions, and discuss the results in Section \ref{sec:conclusions}.

@@

All implementations of the DSD method use high-spectral-resolution and high signal-to-noise spectra, and search for companions with extreme flux ratios by cross-correlating the observed spectra with models for the expected companion. The main differences between the various implementations are the primary star and telluric line removal processes. The `Hot Jupiter' searches \citep[e.g.][]{Snellen2010} use known orbital phase information and a high degree of phase coverage to simultaneously estimate an empirical stellar and telluric spectrum with minimal contamination from the planet, while \cite{Kolbl2015} subtract a best-fit model spectrum for the primary star. Since \cite{Kolbl2015} use optical data, they do not attempt any telluric correction. Note that the approach of \cite{Kolbl2015} is conceptually similar to the todcor code \citep{Mazeh1994}, which is widely used to search for double-lined spectroscopic binary systems.

@@

\begin{equation}
w = \frac{v\sin{i} \cdot f}{c} \cdot \frac{\lambda_0}{\Delta \lambda}
\label{eqn:smoothing}
\end{equation}
where $v\sin{i}$ is the literature rotational velocity of the star, $\lambda_0$ is the central wavelength of the \'echelle order, $\Delta \lambda$ is the wavelength spacing per pixel of the order, $c$ is the speed of light, and $f = 0.25$ is an empirically determined parameter to give a visually adequate fit. Typical window sizes ranged from 50 - 100 pixels.

@@

\begin{itemize}
\item $\rm T_{eff} = 3000-7000$ K\footnote{We extend the grid to higher temperatures if the measured temperature (see Section \ref{subsec:systematics}) is near 7000 K}, in steps of 100 K
\item {[}Fe/H{]} = -0.5, 0.0, +0.5
\item $v\sin{i} = 1, 5, 10, 20, 30 \ \rm km \ s^{-1}$
\end{itemize}
Here, the $v\sin{i}$ is the rotational velocity of the secondary star. We account for the small influence that the smoothing kernel has on the companion spectrum by convolving the model with the same smoothing kernel used for the data, and subtracting the convolved model from the original. Treating the model spectrum in this way is more commonly known as unsharp masking. Finally, we cross-correlate every \'echelle order that does not have strong telluric residuals against the corresponding model spectrum, and combine the CCFs for each order using a simple average. The method is summarized below:

\begin{enumerate}
 \item Smooth the observed spectrum with a Gaussian smoothing kernel with width given by Equation \ref{eqn:smoothing}, and subtract the smoothed spectrum from the original
 \item Rotationally broaden the Phoenix model spectrum to the requested companion $v\sin{i}$
 \item Smooth the broadened spectrum to the instrumental resolution by convolving it with a gaussian kernel of appropriate width.
 \item Unsharp mask the broadened model spectrum
 \item Resample the processed model spectrum to the same wavelength spacing per pixel as the observed spectrum.
 \item Cross-correlate each \'echelle order against the corresponding processed model spectrum, and combine using a simple average.
\end{enumerate}

@@

The second dataset (Table \ref{tab:latecal}) contains F-M type stars which have a high-quality temperature estimate in the literature. We use the first two samples in Sections \ref{subsec:systematics} and \ref{subsec:sensitivity} to assess the accuracy of the temperature estimation using the DSD method and the sensitivity to companions of various temperatures.

@@

We estimate the expected companion temperature depending on whether it is part of a spectroscopic (Table \ref{tab:specdata}) or visual (Table \ref{tab:imagedata}) binary system. In the case of double-lined spectroscopic binaries, we use the ratio of the semi-amplitudes given in the 9th catalog of spectroscopic binary orbits \citep[SB9,][]{SB9} to estimate the mass ratio of the system. We convert the primary star spectral type from the Simbad database \citep{Simbad} to mass by interpolating Table 5 of \citet{Pecaut2013}. The mass ratio and primary mass gives an estimate of the companion mass, which we convert to temperature by interpolating the same table. Most of the directly-imaged binary systems do not have orbital information, so we use the magnitude difference published in the Washington Double Star catalog \citep[WDS, ][]{WDS}. We use the Simbad spectral type of the primary star and Table 5 of \citet{Pecaut2013} to estimate the primary star temperature ($T_1$) and radius ($R_1$). We then find the companion temperature that minimizes the following function for the companion temperature ($T_2$), given the observed magnitude difference ($\Delta m_{obs}$)
\begin{equation}
Q = (m(T_2, R_2) - m(T_1, R_1) - \Delta m_{obs})^2
\label{eqn:secteff}
\end{equation}
where $m(T, R)$ is the Vega magnitude of a star with temperature T and radius R. We use the pysynphot package\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} and a Kurucz model grid \citep{Castelli2003} to calculate $m(T, R)$, and assume the companion is on the main sequence to estimate its radius ($R_2$). For both spectroscopic and visual binary systems, we assume spectral type uncertainties of $\pm 1$ subtype on the primary stars, and propagate the uncertainties into uncertainty in the companion temperature. We include the binary system in the sample if the median companion temperature is $< 7500$ K.

We use the same set of instruments and settings for all observations throughout the three datasets. We use the CHIRON spectrograph \citep{CHIRON} on the 1.5m telescope at Cerro Tololo Inter-American Observatory for all southern targets. This spectrograph is an $R\equiv \lambda / \Delta \lambda = 80000$ cross-dispersed \'echelle spectrograph with wavelength coverage from 450 - 850 nm, and is fed by a $2.7''$ optical fiber. The data are automatically reduced with a standard CHIRON data reduction pipeline, but the pipeline leaves residuals of strong lines in adjacent orders. We bias-correct, flat-field and extract the spectra with the optimum extraction technique \citep{Horne1986} using standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatories, which are operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} tasks, and use the wavelength calibration from the pipeline reduced spectra.

For the northern targets, we use a combination of the High Resolution Spectrograph \citep[HRS,][]{HRS} on the Hobby Eberly Telescope, and the Tull coud\'e \citep[TS23,][]{TS23} and IGRINS \citep{IGRINS} spectrographs, both on the 2.7m Harlan J. Smith Telescope. All three northern instruments are at McDonald Observatory. For the HRS, we use the $R = 60000$ setting with a $2''$ fiber, and with wavelength coverage from 410-780 nm. We bias-correct, flat-field, and extract the spectra using an IRAF pipeline. The HRS spectra are wavelength-calibrated using a Th-Ar lamp observed immediately before or after the science observations.

For the TS23, we use a $1.2''$ slit in combination with the E2 \'echelle grating (53 grooves/mm, blaze angle $65^{\circ}$), yielding a resolving power of $R=60000$ and a wavelength coverage from 375-1020 nm. We reduce the data using an IRAF pipeline very similar to the one we use for the HRS, and wavelength calibrate using a Th-Ar lamp observed immediately before the science observations.

@@

\begin{figure}
        \centering
        \subfigure[TS23]{
            \label{fig:error:a}
            \includegraphics[scale=0.45]{TS23_simple_Tact2Tmeas.pdf}
         }
         \subfigure[HRS]{
             \label{fig:error:b}
             \includegraphics[scale=0.45]{HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{fig:error:c}
             \includegraphics[scale=0.45]{IGRINS_simple_Tact2Tmeas.pdf}
         }
         \subfigure[CHIRON]{
             \label{fig:error:d}
             \includegraphics[scale=0.45]{CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectral detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subsec:systematics}), and the blue lines are the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{fig:error}
\end{figure}

@@

Each synthetic binary observation contributes a pair of measured and actual (literature) companion temperatures, and so each late-type star in Table \ref{tab:latecal} has many independent temperature measurements made with the DSD method. To determine the correspondence between measured and actual temperature, we perform a Markov Chain Monte Carlo (MCMC) fit to a straight line using the emcee code \citep{emcee}. We plot the mean and standard deviation of the measured temperatures in Figure \ref{fig:error}, along with 300 MCMC samples for the linear fit and the line of unity slope. The MCMC samples give posterior probability distributions for the parameters $a$ and $b$ relating the actual temperature ($T_a$) to the measured temperature ($T_m$) through

@@

The typical temperature uncertainty with the DSD method is $\sim 150 - 200$ K, but the optical instruments systematically overestimate the companion temperature. \emph{The error analysis is therefore not just important to measure the parameter uncertainties, but also to get the correct answer.} We suspect the systematic biases come from a mismatch between the Phoenix model spectrum template and the real spectrum of a late-type star. The biases are different for each instrument because the instruments have different wavelength ranges, and so the spectral lines that contribute most to the cross-correlation function are different.

@@

By combining the sensitivity calculations described above with the $v\sin{i}$ samples, we marginalize over the expected rotation periods of the secondary stars to get simpler curves of detection rate as a function of companion star temperature. We show the median and approximate range of the marginalized detection rate in Figure \ref{fig:sensitivity}. The DSD method can reliably detect companions as cool as 3700 K in most cases, although the primary star spectral type plays a dominant role in setting the coolest detectable companion.

@@

We now use the DSD method to measure the temperatures of several known binary systems (Table \ref{tab:known}). We cross-correlate the spectra against the full grid of model spectra enumerated in Section \ref{sec:method}, and find the temperature using Equation \ref{eqn:tmeas}. We then convert the measured temperature to PDFs of the true companion temperature using the MCMC chains developed in Section \ref{subsec:systematics} (see also Figure \ref{fig:error}). For stars with multiple observations, we multiply the PDFs from each detection. Finally, we calculate the companion temperature and confidence interval from the integral of the PDF:

@@

We compare our companion temperature measurements from the DSD method to the estimates described above in Figure \ref{fig:known}. There is overall excellent agreement between the temperatures, with most points falling within $1 \sigma$ of equality. We test for a bias ($\Delta$) between the measured temperatures ($T_m$) and expected temperatures ($T_a$) with the equations

@@

\section{Discussion and Conclusions}
\label{sec:conclusions}
We have presented and extensively characterized the direct spectral detection method for finding companions to intermediate-mass stars using high-resolution cross-dispersed \'echelle spectroscopy. Using a very large number of synthetic but realistic binary star observations, we constrained the uncertainty and systematic errors present in determining the companion temperature with the direct spectral detection method. The typical uncertainties are of the order of 200 K across all instruments used in this study, with a systematic offset of similar magnitude (for the optical instruments). We used the synthetic binary star analysis to calibrate the direct spectral detection method for the four instruments used in this study between the temperatures $ 3500\ K < T < 6500\ K$.

We also estimated the sensitivity to detection of companions with a range of temperature and $v\sin{i}$ by creating a second set of synthetic companions. The method can detect companions as late as M0 in most cases, although the lower limit depends on the primary star spectral type, the signal-to-noise ratio achieved, and the instrument used. The median detection limit corresponds to average flux ratios as small as $F_{\rm  sec}/F_{\rm prim} \sim 10^{-3}$ and binary mass-ratios $M_{\rm  sec}/M_{\rm prim} \sim 0.2$, or a main-sequence M0 star orbiting an A0V primary.

The lowest detectable mass ratio is even more striking for young stars. At 1 Myr, both the A0 star and its companion are still contracting onto the main sequence \citep{Bressan2012}. The flux ratio limit corresponds to a $\sim$ M1 companion, similar to the main sequence case. However the mass ratio in this young system is $M_{\rm  sec}/M_{\rm prim} \sim 0.1$, half that of main-sequence components with similar spectral types. The direct spectral detection method is therefore well suited for finding close, low-mass companions to massive young stars.

There is also an upper detection limit near $6500\ K$ set by rotation. Our method of removing the primary star spectrum can also remove the companion spectrum if it has a similar rotational velocity, which hot companions are likely to have. Subtracting a model atmosphere for the primary star would remove the upper limit, but would reduce the detection rate for cool companions that are most difficult to detect with any other means.

Finally, we applied the direct spectral detection method to a set of known binary systems with close, late-type companions. We detected the companion spectrum in 9 of 34 known binary systems, 3 of which we characterized for the first time. Most of the companions we failed to detect are likely very cool, falling below the sensitivity limit of our data.

@@

The Hobby-Eberly Telescope (HET) is a joint project of the University of Texas at Austin, the Pennsylvania State University, Stanford University, Ludwig-Maximilians-Universit\"at M\"unchen, and Georg-August-Universit\"at G\"ottingen. The HET is named in honor of its principal benefactors, William P. Hobby and Robert E. Eberly.

@@

Finally, we would like to thank the anonymous referee for numerous comments that improved the paper.

@@

\enddata
%\vspace{-0.8cm}
\tablecomments{Known binary stars detected through either high-contrast imaging or interferometry. The imaging data comes from the Washington Double Star Catalog \citep{WDS}, and the most recent measurements are given as superscripts to the star name: [1]: \cite{McAlister1989}; [2]: \cite{Roberts2007}; [3]: \cite{Hipparchos}; [4]: \cite{Mamajek2010}; [5]: \cite{Drummond2014}; [6]: \cite{Shatsky2002}; [7]: \cite{Tokovinin2010}; [8]: \cite{McAlister1987}; [9]: \cite{Horch2010}; [10]: \cite{Horch2008}; [11]: \cite{Horch2001}; [12]: \cite{DeRosa2012}
}
\end{deluxetable}

@@

\newpage
\clearpage
\bibliography{references}
